### 2018-02-08 usenix18/ex.tex
formatting
space crunches.
some more minor edits.

\section{\tool Overview}
\label{sec:ex}
%$w^Tx>0$, mnist logistic regression
%% \divya{add reference to before and later... as mentioned we would run evaluations on secure prediction of different models. Here we describe scenario in detail..}

@@

\figureref{toolchain} shows an overview of the \tool
toolchain. We give a brief overview of each of these phases below.

\paragraph{Source language.}
Consider the example $w^Tx >b$ from \sectionref{intro}, where
$w$ and $b$ constitute the server's input (a classifier) and $x$ is
the client's input vector. \figureref{ex-sml} shows the \tool code
for this example. The code first reads the server's (resp. client's) input using
 \ls{input1} (resp. \ls{input2}). It then uses a
\ls{for} loop to compute \ls{acc}, the inner product of \ls{w} and
\ls{x}. Finally, the code outputs the result of comparing \ls{acc}
with \ls{b} only to the client using \ls{output2}.

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.

\paragraph{\tool compiler.}
\tool compiler takes as input a source program and produces a C++
program as output. \figureref{ex-aby} shows the output code\footnote{This is also how a program written directly in
  ABY would look like.} for
the example in \figureref{ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

@@

Using both arithmetic and boolean representations requires conversions between them.
The \tool compiler also
instruments these conversion gates accordingly. For example, in
lines~\ref{line:convacc} and~\ref{line:convb}, the compiler converts
\ls{a\_acc} and \ls{a\_b} to boolean representation, before they are
input to the comparison and multiplexer circuits.

\begin{figure}
\begin{lstlisting}[language=C, mathescape=true]
//circuit builders for arithmetic and boolean
$\mathtt{
Circuit\;*ycirc = s[S\_YAO]\rightarrow GetCircuitBuildRoutine();
}$
$\mathtt{
Circuit\;*acirc = s[S\_ARITH]\rightarrow GetCircuitBuildRoutine();
}$
$\dots$
$\mathtt{
if(role == SERVER)\;\{ 
}$
  //Put gates to read w and b
$\mathtt{
\}\;else\;\{\;\;\textbf{{\color{blue}//role == CLIENT}}
}$  
  //Put gates to read x
$\mathtt{
\}
}$

@@

\paragraph{Circuit generation and evaluation.} The next step in
\tool is to
compile the output C++ code and execute it. Doing so evaluates away the
public parts of the program, including the array accesses, and
generates a  circuit comprising of arithmetic and boolean gates,
with appropriate conversion gates. The circuit is then evaluated using
a \mpc protocol.

We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program and get right the code in
\figureref{ex-sml}, rather than the code in
\figureref{ex-aby}.
% (as we mentioned in Section~\ref{sec:intro},
%other high-level languages are limited in their use of a single,
%arithmetic or boolean, crypto back-end). 
\tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in \figureref{ex-sml} a
change from multiplication to bitwise-or in the \ls{for} loop. It
turns out that once that's the case, it is more efficient to do both
the addition and bitwise-or using boolean circuits (if the addition is
still done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or she would have to
revisit many parts of the circuit and change them.

To summarize, \tool raises the level of abstraction for the
programmer, and generates efficient \mpc protocols automatically,
while its metatheory provides strong correctness and security
guarantees.

>>>>

\vspace{-0.1in}
\section{\tool Overview}
\label{sec:ex}
%$w^Tx>0$, mnist logistic regression
%% \divya{add reference to before and later... as mentioned we would run evaluations on secure prediction of different models. Here we describe scenario in detail..}

@@

\figureref{toolchain} shows an overview of the \tool
toolchain. We give a brief overview of each of these phases below.
\vspace{-0.15in}
\paragraph{Source language.}
Consider the example $w^Tx >b$ from \sectionref{intro}, where
$w$ and $b$ are the server's input (a classifier) and $x$ is
the client's input vector. \figureref{ex-sml} shows the \tool code
for this example. The code first reads the server's (resp. client's) input using
 \ls{input1} (resp. \ls{input2}). It then uses a
\ls{for} loop to compute \ls{acc}, the inner product of \ls{w} and
\ls{x}. Finally, the code compares \ls{acc}
with \ls{b} and outputs this only to the client using \ls{output2}.

\tool source language is a simple, imperative language that enables
the programmers to express \mpc computations in terms of their
``ideal'' functionalities, without dealing with any cryptographic
details. The language provides multi-dimensional arrays, conditional
expressions (the ternary $?\::$ operator), \ls{for}~loops,
\ls{if}~statements, and special syntax for input/output from each party.
\vspace{-0.1in}
\paragraph{\tool compiler.}
\tool compiler takes as input a source program and produces a C++
program as output. \figureref{ex-aby} shows the output code\footnote{This is also how a program written directly in
  ABY would look like.} for
the example in \figureref{ex-sml}. The output program
contains party-specific code for inputs and outputs
(\ls{role == SERVER} and \ls{role == CLIENT}), and common code for the
computation.

@@

Using both arithmetic and boolean representations requires conversions between them.
The \tool compiler also
instruments these conversion gates accordingly. For example, in
lines~\ref{line:convacc} and~\ref{line:convb}, the compiler converts
\ls{a\_acc} and \ls{a\_b} to boolean representation, before they are
input to the comparison and multiplexer circuits.
\vspace{-0.2in}
\begin{figure}[h]
\begin{lstlisting}[language=C, mathescape=true]
//circuit builders for arithmetic and boolean
$\mathtt{
Circuit\;*ycirc = s[S\_YAO]\rightarrow GetCircuitBuildRoutine();
}$
$\mathtt{
Circuit\;*acirc = s[S\_ARITH]\rightarrow GetCircuitBuildRoutine();
}$
$\dots$
$\mathtt{
if(role == SERVER)\;\{ 
}$
  //Put gates to read w and b
$\mathtt{
\}\;else\;\{\;\;\textbf{{\color{blue}//role == CLIENT}}
}$  
  //Put gates to read x
$\mathtt{
\}
}$

@@

\paragraph{Circuit generation and evaluation.} The next step in
\tool is to
compile the output C++ code and execute it. Doing so evaluates away the
public parts of the program, including the array accesses, and
generates a  circuit comprising of arithmetic and boolean gates,
with appropriate conversion gates. The circuit is then evaluated using
a \mpc protocol.
\vspace{-0.1in}
\paragraph{Advantages of \tool.} We can now concretely see the advantages of \tool. Unarguably, it is
easier for a developer to program and get the code right in
\figureref{ex-sml}, rather than the code in
\figureref{ex-aby}.
% (as we mentioned in Section~\ref{sec:intro},
%other high-level languages are limited in their use of a single,
%arithmetic or boolean, crypto back-end). 
\tool also enables the
programmer to easily modify their code, while the compiler takes care
of efficiency. For example, consider in \figureref{ex-sml} a
change from multiplication to bitwise-or in the \ls{for} loop. It
turns out that in this case, it is more efficient to do both
the addition and bitwise-or using boolean circuits (if the addition is
done using arithmetic, the conversion cost starts to take
over). In \tool, the programmer simply needs to change one operator in
the source code, and the compiler generates efficient code that uses
boolean addition. Whereas, if the programmer was writing ABY
code, she either has to sacrifice performance, or would have to
revisit many parts of the circuit and change them. In summary, \tool raises the level of abstraction for the
programmer, and generates efficient \mpc protocols automatically,
while its metatheory provides strong correctness and security
guarantees.
